---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->  

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, fig.path = "README-", 
                      eval = TRUE)
library(spcmap)

```

# spcmap
An R package to map coordinates with 'NOAA' Storm Prediction Center severe weather risks

## Introduction
This is a small package that contains a few functions to plot coordinates of interest
against the [NOAA Storm Prediction Center](http://www.spc.noaa.gov/) (SPC) outlooks

## Installation
The package can be installed via the `devtools` package:
```
devtools::install_github("neyhartj/spcmap")
```

## Examples

The package contains one primary function, `spcmap` and a few secondary supporting
functions. 

Say you have a set of coordinates that you want to map:

```{r coord}
dat <- data.frame(
  city = c("MSP", "JFK", "LAX"),
  long = c(-93.17567, -74.0071, -118.2453),
  lat = c(44.98231, 40.7146, 34.0535)
)

```

Use the `spcmap` function to download the SPC data for a particular day and type.
This function downloads a `.kml` file from the Storm Prediction Center 
[website](http://www.spc.noaa.gov/gis/). You can download data for the current 
day or up to two days in the future. Outlook types include categorical, tornado, 
hail, and wind. The following table outlines the codes:

  Type         Outlook
---------   ----------------
  `cat`       categorical
  `torn`      tornado
  `hail`      hail
  `wind`      wind
  
For example, let's find the categorical data for day 1

```{r spcmap}
spc <- spcmap(data = dat, day = 1, type = "cat")

```


You can use the `summary()`, `print()`, and `plot()` functions to explain or
plot the results.

```{r explain}
# Summary
summary(spc)
```

```{r plot}
# Plot
plot(spc)

```

## Notes

In accordance with the 'NOAA'/'NWS'
[disclaimer](http://www.weather.gov/disclaimer), please note that this R package 
is in no way affiliated with 'NOAA' and has not been endorsed by 'NOAA.' The 
information provided in the package is not official government information. I
claim no copyright over for the information provided by 'NOAA.'

## Author
Jeff Neyhart
